PANCHANGE_descriptives

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added phq scatterplots for little/much worse prepan retro scores for phq

@@

#Correlation little/much worse prepan retro gad

@@

```{r Little/much worse scatterplots for gad}

@@

#Filter by little/much worse self-reported change since pandemic started in gad

much_worse_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much worse")

little_worse_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "A little worse")

much_little_worse_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much worse" | 
           gad.pandemic_felt_feelings == "A little worse")

@@

@@

#Little/much better prepan retro correlation

>>>>

###Whole sample prepan retro correlation

@@

###Little/much worse prepan retro correlation

@@

```{r Little/much worse prepan retro scatterplot prep}

@@

#Filter by little/much worse self-reported change since pandemic started in gad and phq

much_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
  filter(gad.pandemic_felt_feelings == "Much worse")

little_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
  filter(gad.pandemic_felt_feelings == "A little worse")

much_little_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
  filter(gad.pandemic_felt_feelings == "Much worse" | 
           gad.pandemic_felt_feelings == "A little worse")

much_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
  filter(phq.pandemic_felt_feelings == "Much worse")

little_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
  filter(phq.pandemic_felt_feelings == "A little worse")

much_little_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
  filter(phq.pandemic_felt_feelings == "Much worse" | 
           phq.pandemic_felt_feelings == "A little worse")

```{r Little/much worse prepan retro scatterplots}

@@

much_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse",
                      sep=" "),
        subtitle = paste("n", dim(much_worse_phq_scatter)[1]))

little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little worse",
                      sep=" "),
        subtitle = paste("n", dim(little_worse_phq_scatter)[1]))

much_little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse and a little worse",
                      sep=" "),
        subtitle = paste("n", dim(much_little_worse_phq_scatter)[1]))

@@

###Little/much better prepan retro correlation
